\textbf{ Mapping stellar surfaces\\ I: Degeneracies in the rotational light curve problem }

### 2021-01-25 paper1/ms.tex
almost there...

\xxx{In this section, we define and present some demonstrations of the null space and how it can affect inferences about stellar surfaces.
    We also present some examples of how these issues can be tackled.
    While these specific examples may appear somewhat idealized, at the end of this section, we discuss how these ideas generalize to more realistic scenarios.
    This is also a topic that we discuss in much more detail in \citetalias{PaperII}.}

@@

\section{The baseline problem}
\label{sec:baseline}

\subsection{A fundamental issue of units}

@@

To understand this degeneracy, consider how we might go about simulating
a stellar surface.
%
We might add a dark spot somewhere on the surface, either by expanding
it in spherical harmonics or by gridding up the stellar surface and
setting the intensity of pixels within the spot to a low value. To compute
the light curve, we integrate over the
projected disk at each point in time.
% , either analytically (if we're
% in the spherical harmonic basis) or numerically by computing a weighted
% sum of the visible pixels (if we're in the pixel basis).
The resulting
light curve will have strange units, so we might then divide by the
integral of the background intensity over the unit disk, so that we are
now in what we will call \emph{fractional units}: the flux as a
fraction of the flux we would measure if the star had no spots on it.

>>>>

In this section, we define the concept of the \emph{null space}
and present some demonstrations showing how it can affect inferences
about stellar surfaces.
We also present some examples of how the degeneracies due to
the null space can be tackled.
While our specific examples may appear somewhat idealized, at the end
of this section we discuss how our ideas generalize to more
realistic scenarios.
This is also a topic that we discuss in much more detail in \citetalias{PaperII}.

@@

\section{The baseline degeneracy}
\label{sec:baseline}

@@

\subsection{A fundamental issue of units}
%
To understand the baseline degeneracy, consider how we might go about simulating
a stellar surface.
%
We might add a dark spot somewhere on the surface, either by expanding
it in spherical harmonics or by gridding up the stellar surface and
setting the intensity of pixels within the spot to a low value. To compute
the light curve, we integrate over the
projected disk at each point in time.
% , either analytically (if we're
% in the spherical harmonic basis) or numerically by computing a weighted
% sum of the visible pixels (if we're in the pixel basis).
The resulting
light curve will have strange units, so we might then divide by the
integral of the background intensity over the unit disk, so that we are
now in what we will call \emph{fractional units}: the flux as a
fraction of the flux we would measure if the star had no spots on it.
